Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2012-03-05 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2012:03:05	13:28:57	(Mon 5.Mar)
la2pdf commit - 2012:03:05	14:00:44	(Mon 5.Mar)

\newif\ifPeerReview \PeerReviewfalse            % Whether to create the PeerReview version or
                                                % Journal version
\newif\ifFlatArchive\FlatArchivefalse           % Whether archive is flat (messy) or contain 
                                                % subfolders for graphics etc.
\newif\ifFloatAtEnd\FloatAtEndfalse             % Available in PeerReview mode:
                                                % Place floats at end of document?
\newif\ifTODO\TODOtrue                          % Use todo notes?

@@

@@

\ifTODO
   \definecolor{lightblue}{rgb}{0.8,0.8,1}
   \usepackage[backgroundcolor=LightBlue]{todonotes}
\else
   \usepackage[disable]{todonotes} 
\fi

@@

%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% DOCUMENT START %
%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\begin{document}
%
\title{Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging}

@@

\IEEEPARstart{A}{daptive} beamformers have only recently been introduced in active sonar imaging.\todo[inline]{break} This is because , as demo file is intended to serve as a ``starter file''
for IEEE Computer Society journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

>>>>

\newif\ifPeerReview\PeerReviewfalse             % Whether to create the PeerReview version or
                                                % Journal version
\newif\ifFlatArchive\FlatArchivefalse           % Whether archive is flat (messy) or contain 
                                                % subfolders for graphics etc.
\newif\ifFloatAtEnd\FloatAtEndfalse             % Available in PeerReview mode:
                                                % Place floats at end of document?
\newif\ifTODO\TODOtrue                         % Use todo notes?

@@

\ifTODO
   \setlength{\marginparwidth}{1cm}
%    \setlength{\marginparpush}{1cm}
   \setlength\textwidth{\columnwidth}
   \addtolength\marginparsep{1.5cm}
   \definecolor{lightblue}{rgb}{0.8,0.8,1}
   \usepackage[backgroundcolor=LightBlue]{todonotes}
\else
   \usepackage[disable]{todonotes} 
\fi

@@

@@

%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% DOCUMENT START %
%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  \RequirePackage{layout}  
\begin{document}
\layout
%
\title{Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging}

@@

\IEEEPARstart{A}{daptive} beamformers have only recently been introduced in active sonar imaging.{\todo{break at something}} This is because , as demo file is intended to serve as a ``starter file''
for IEEE Computer Society journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.
